SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-05-13 scipy-1.0/paper.tex
Attempt to incorporate @ilayn's comments
"I think being a maintainer is a bit more long-term and involved (still of course anyone can become) so we might not want to paint the wrong picture about that here." - @ilayn
"You can start with the definition of a maintainer and then switch to SciPy specific details. Also approximately 15 is in fact exactly 15" @ilayn
I didn't want to lead with a separate definition; I think it is more compact and immediately relevant if the definition is provided in-line. I do prefer a colon over the em dash, though, if only to ovoid overuse of the em dash.

\subsection*{Downstream projects}

The scientific Python ecosystem includes many examples
of domain-specific software libraries that are built 
on top of SciPy features. The work done on these libraries
often turns out to be beneficial to the whole ecosystem
being SciPy the catalyst of this cross-fertilisation process. 
For example, there are common contributors to the SciPy and 
Astropy core libraries\cite{astropy-2018}, and what works 
well for one of the codebases, infrastructures, or communities 
is often transferred in some form to the other. At the codebase 
level, the \texttt{binned\_statistic} functionality
is one such cross-project contribution---it was initially
developed in an Astropy-affiliated package
and then placed in SciPy afterwards.

@@

The SciPy project has approximately 15 active maintainers---people who review
others' contributions, and in general do everything needed to ensure that the
software and the project move forward. Maintainers are critical to the health
of the project\cite{eghbal2016}; their skills and efforts largely determine how
fast the project moves forward, and they enable contributions from a much
larger group. Accordingly, the project also has an additional ~100 unique
contributors for every 6-monthly release cycle. Anyone with the interest and
skills can become a contributor or maintainer; the SciPy Developer
Guide\cite{scipy-dev-guide} provides guidance on how to do that.

>>>>

@@

The SciPy project has approximately 100 unique contributors
for every 6-monthly release cycle. Anyone with the interest and
skills can become a contributor; the SciPy Developer
Guide\cite{scipy-dev-guide} provides guidance on how to do that.
In addition, the project currently has 15 active maintainers: people who review
the contributions of others and do everything else needed to ensure that the
software and the project move forward. Maintainers are critical to the health
of the project\cite{eghbal2016}; their skills and efforts largely determine how
fast the project moves forward, and they enable input from the much
larger group of contributors. Anyone can become a maintainer, too, as they
are selected on a rolling basis from contributors with a significant history of
high-quality contributions.

\subsection*{Community beyond the SciPy library}

The scientific Python ecosystem includes many examples
of domain-specific software libraries building on top
of SciPy features, and then returning to the base SciPy library
to suggest and even implement improvements to enable
more effective science applications. For example, there
are common contributors to the SciPy and Astropy core
libraries\cite{astropy-2018}, and what works well for 
one of the codebases, infrastructures, or communities 
is often transferred in some form to the other. At the codebase 
level, the \texttt{binned\_statistic} functionality
is one such cross-project contribution---it was initially
developed in an Astropy-affiliated package
and then placed in SciPy afterwards.
